Reviewers' Decision to Sign Reviews is Related to Their Recommendation

### 2020-06-04 manuscript/revision_2/open_peer_review.Rmd
accepted version of the manuscript

---
title             : "Reviewers' Decision to Sign Reviews is Related to Their Recommendation"
shorttitle        : "Signing Open Reviews"
author: 
  - name          : "Nino van Sambeek"
    affiliation   : "1"
  - name          : "Daniel Lakens"
    affiliation   : "1"
    corresponding : yes
    address       : "ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology, The Netherlands"
author_note: |
 Submitted to Meta-Psychology. Click here to follow the fully transparent editorial process of this submission. Participate in open peer review by commenting through hypothes.is directly on this preprint. This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/9526a/
abstract: |
 Surveys indicate that researchers generally have a positive attitude towards open peer review when this consists of making reviews available alongside published articles. Researchers are more negative about revealing the identity of reviewers. They worry reviewers will be less likely to express criticism if their identity is known to authors. Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be communicated to authors, than when they will remain anonymous. One recent study revealed reviewers in five journals who voluntarily signed their reviews gave more positive recommendations than those who did not sign their reviews. We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews. These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers' decision to sign is related to their recommendation. The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations. We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.

@@

For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round. Note that for PeerJ the editor makes the recommendation for each submission based on the reviews. We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews. For Royal Society Open journals reviewers do recommend to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'. Because PeerJ and Royal Society Open journals only share reviews for published articles there are few 'reject' recommendations for Royal Society Open journals and no 'reject' recommendations by editors among PeerJ reviews. Searching all reviews for PeerJ for the words 'appealed on' revealed 47 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published. We have coded these papers as 'major revisions'. All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at https://osf.io/9526a/.

@@

Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of 'accept', 'minor revisions', 'major revisions', or 'reject'. We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}). The overall pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).

@@

Both PeerJ as Royal Society Open journals publish articles in a wide range of disciplines, including astronomy, biochemistry, chemistry, computer science, earth science, ecology, engineering, genomics, mathematics, evolutionary biology, paleontology, physics, psychology, and zoological science. The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available for Royal Society Open journals.

```{r, echo=FALSE, results='asis'}
cat("\\onecolumn")
```

@@

```{r, echo=FALSE, results='asis'}
cat("\\twocolumn")
```

To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section). We see the general pattern holds across all fields. In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned. Beyond this main effect, we see a clear interaction across all sections, where the ratio of signed versus unsigned reviews is consistently greater for major revisions than for minor revisions. Across all fields covered by PeerJ, it is relatively less likely to see a signed review for major revisions than for minor revisions, suggesting that the observed effect is present across disciplines.

Figure \ref{fig:recperyear} shows the number of signed and unsigned reviews as a function of the recommendation for each year in which articles were published (since 2012 for PeerJ, and since 2014 for Royal Society Open journals). As already noted, the proportion of signed reviews reduced over time compared to earlier analyses by @wang_open_2016. Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals. It seems that in the early years that these journals existed, more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews. We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts. As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science, to include reviewers less likely to sign their reviews.

@@

Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected. As a consequence, we have analyzed a biased sample of the literature. Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000). Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal. Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.

@@

Reviewers might have different reasons to sign or not sign their reviews. They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission. Reviewers might not want to reveal how their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest. Finally, reviewers might fear backlash from authors who receive their negative reviews. Our data supports the idea that reviewers' decisions to sign are related to their recommendation across a wide range of scientific disciplines. Due to the correlational nature of the data, this relationship could emerge because reviewers who are on average more likely to sign also give more positive recommendations, reviewers are more likely to sign more positive recommendations, or both these effects could be true at the same time. Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some reviewers are more likely to sign if their recommendation is more positive. This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs. For positive recommendations, reviewers will get credit for their reviews, while for negative reviews they do not run the risk of receiving any backlash from colleagues in their field.

@@

## ORCID iD

>>>>

---
title             : "Reviewers' Decision to Sign Reviews is Related to Their Recommendation"
shorttitle        : "Signing Open Reviews"
author: 
  - name          : "Nino van Sambeek"
    affiliation   : "1"
  - name          : "Daniel Lakens"
    affiliation   : "1"
    corresponding : yes
    address       : "ATLAS 9.402, 5600 MB, Eindhoven, The Netherlands"
    email         : "D.Lakens@tue.nl"
affiliation:
  - id            : "1"
    institution   : "Eindhoven University of Technology, The Netherlands"
author_note: |
 Accepted for publication at Meta-Psychology. This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/9526a/. A Code Ocean capsule that computationally reproduces this manuscript is available at https://codeocean.com/capsule/6067104.
abstract: |
 Surveys indicate that researchers generally have a positive attitude towards open peer review when this consists of making reviews available alongside published articles. Researchers are more negative about revealing the identity of reviewers. They worry reviewers will be less likely to express criticism if their identity is known to authors. Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be communicated to authors, than when they will remain anonymous. One recent study revealed reviewers in five journals who voluntarily signed their reviews gave more positive recommendations than those who did not sign their reviews. We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews. These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers' decision to sign is related to their recommendation. The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations. We also share all 23649 text-mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.

@@

For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round. Note that for PeerJ the editor makes the recommendation for each submission based on the reviews. We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews. For Royal Society Open journals reviewers make a recommendation, which may be to 'accept as is', 'accept with minor revisions', 'major revision', or 'reject'. Because PeerJ and Royal Society Open journals only share reviews for published articles there are few 'reject' recommendations for Royal Society Open journals and no 'reject' recommendations by editors among PeerJ reviews. Searching all reviews for PeerJ for the words 'appealed on' revealed 47 articles that were initially rejected, appealed, received a 'major revision' recommendation, and were eventually published. We have coded these papers as 'major revisions'. All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at https://osf.io/9526a/.

@@

Analyzing the reviews at Royal Society Open journals provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of 'accept', 'minor revisions', 'major revisions', or 'reject'. We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}). The overall pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).

@@

Both PeerJ and Royal Society Open journals publish articles in a wide range of disciplines. The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available from meta-data or the bibliographic record for Royal Society Open journals.

\onecolumn

@@

\twocolumn

To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section). We see that the general pattern holds across all fields. In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned. Beyond this main effect, we see a clear interaction across all sections, where the ratio of signed versus unsigned reviews is consistently greater for major revisions than for minor revisions. Across all fields covered by PeerJ, it is relatively less likely to see a signed review for major revisions than for minor revisions, suggesting that the observed effect is present across disciplines.

Figure \ref{fig:recperyear} shows the number of signed and unsigned reviews as a function of the recommendation for each year in which articles were published (since 2012 for PeerJ, and since 2014 for Royal Society Open journals). As already noted, the proportion of signed reviews reduced over time compared to earlier analyses by @wang_open_2016. Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals. It seems that in the early years of their existence more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews. We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts. As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science, to include reviewers less likely to sign their reviews.

@@

Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected. As a consequence, we have analyzed a biased sample of the literature. Few scientific journals make peer reviews available for all submitted articles (two notable exceptions are Meta-Psychology and F1000). Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal. Despite this limitation, the pattern of results we observe is very similar to that reported by @bravo_effect_2019 who had access to the reviews for accepted and rejected manuscripts.

@@

Reviewers might have different reasons to sign or not sign their reviews. They might be worried about writing a positive review for a paper that is later severely criticized, and receiving blame for missing these flaws when reviewing the submission. Reviewers might not want to reveal that their recommendations are unrelated to the scientific quality of the paper, but based on personal biases or conflicts of interest. Finally, reviewers might fear backlash from authors who receive their negative reviews. Our data supports the idea that reviewers' decisions to sign are related to their recommendation across a wide range of scientific disciplines. Due to the correlational nature of the data, this relationship could emerge because reviewers who are on average more likely to sign also give more positive recommendations, reviewers are more likely to sign more positive recommendations, or both these effects could be true at the same time. Together with self-report data and experiments reported in the literature, our data increase the plausibility that in real peer reviews at least some reviewers are more likely to sign if their recommendation is more positive. This type of strategic behavior also follows from a purely rational goal to optimize the benefits of peer review while minimizing the costs. For positive recommendations, reviewers will get credit for their reviews, while for negative reviews they do not run the risk of receiving any backlash from colleagues in their field.

@@

## ORCID ID

### 2020-06-04 manuscript/revision_2/open_peer_review.tex
accepted version of the manuscript

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Signing Open Reviews}
\author{Nino van Sambeek\textsuperscript{1}\ \& Daniel Lakens\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology, The Netherlands}
\authornote{Submitted to Meta-Psychology. Click here to follow the fully transparent editorial process of this submission. Participate in open peer review by commenting through hypothes.is directly on this preprint. This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/9526a/

@@

\abstract{
Surveys indicate that researchers generally have a positive attitude towards open peer review when this consists of making reviews available alongside published articles. Researchers are more negative about revealing the identity of reviewers. They worry reviewers will be less likely to express criticism if their identity is known to authors. Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be communicated to authors, than when they will remain anonymous. One recent study revealed reviewers in five journals who voluntarily signed their reviews gave more positive recommendations than those who did not sign their reviews. We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews. These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers' decision to sign is related to their recommendation. The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations. We also share all 23649 text mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
}

@@

PeerJ assigns all articles a number, increasing consecutively with each published manuscript. Reviews are always accessible in HTML (e.g., reviews for the first article published in PeerJ are available at \url{https://peerj.com/articles/1/reviews}). For Royal Society Open journals reviews are published online as a PDF file. A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus. All available reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2019; R Core Team, 2013). These text files were mined for recommendations, reviewer names, submission and acceptance dates, and the review content, using the stringr package in R (Wickham, 2019).

For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round. Note that for PeerJ the editor makes the recommendation for each submission based on the reviews. We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews. For Royal Society Open journals reviewers do recommend to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}. Because PeerJ and Royal Society Open journals only share reviews for published articles there are few \enquote{reject} recommendations for Royal Society Open journals and no \enquote{reject} recommendations by editors among PeerJ reviews. Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 47 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published. We have coded these papers as \enquote{major revisions}. All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at \url{https://osf.io/9526a/}.

@@

Analyzing the reviews at the Royal Society provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}. We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}). The overall pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).

@@

Both PeerJ as Royal Society Open journals publish articles in a wide range of disciplines, including astronomy, biochemistry, chemistry, computer science, earth science, ecology, engineering, genomics, mathematics, evolutionary biology, paleontology, physics, psychology, and zoological science. The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available for Royal Society Open journals.

@@

To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section). We see the general pattern holds across all fields. In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned. Beyond this main effect, we see a clear interaction across all sections, where the ratio of signed versus unsigned reviews is consistently greater for major revisions than for minor revisions. Across all fields covered by PeerJ, it is relatively less likely to see a signed review for major revisions than for minor revisions, suggesting that the observed effect is present across disciplines.

Figure \ref{fig:recperyear} shows the number of signed and unsigned reviews as a function of the recommendation for each year in which articles were published (since 2012 for PeerJ, and since 2014 for Royal Society Open journals). As already noted, the proportion of signed reviews reduced over time compared to earlier analyses by Wang et al. (2016). Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals. It seems that in the early years that these journals existed, more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews. We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts. As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science, to include reviewers less likely to sign their reviews.

@@

Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected. As a consequence, we have analyzed a biased sample of the literature. Few scientific journals make peer reviews available for all submitted articles (for notable exceptions, see Meta-Psychology and F1000). Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal. Despite this limitation, the pattern of results we observe is very similar to that reported by Bravo et al. (2019) who had access to the reviews for accepted and rejected manuscripts.

@@

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

@@

\hypertarget{conflict-of-interest-statement}{%
\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}

@@

\hypertarget{funding}{%
\section{Funding}\label{funding}}

@@

\hypertarget{orcid-ids}{%
\subsection{ORCID iD's}\label{orcid-ids}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bastian_signing_2018}{}%
Bastian, H. (2018). Signing Critical Peer Reviews \& the Fear of Retaliation: What Should We Do? \textbar{} Absolutely Maybe. https://blogs.plos.org/absolutely-maybe/2018/03/22/signing-critical-peer-reviews-the-fear-of-retaliation-what-should-we-do/.

@@

\leavevmode\hypertarget{ref-ooms_pdftools_2019}{}%
Ooms, J. (2019). \emph{Pdftools: Text extraction, rendering and converting of PDF documents}.

@@

\leavevmode\hypertarget{ref-wickham_stringr_2019}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}.

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Signing Open Reviews}
\author{Nino van Sambeek\textsuperscript{1}\ \& Daniel Lakens\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology, The Netherlands}
\authornote{Accepted for publication at Meta-Psychology. This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013. All data underlying this reproducible manuscript are available at https://osf.io/9526a/. A Code Ocean capsule that computationally reproduces this manuscript is available at https://codeocean.com/capsule/6067104.

@@

\abstract{
Surveys indicate that researchers generally have a positive attitude towards open peer review when this consists of making reviews available alongside published articles. Researchers are more negative about revealing the identity of reviewers. They worry reviewers will be less likely to express criticism if their identity is known to authors. Experiments suggest that reviewers are somewhat less likely to recommend rejection when they are told their identity will be communicated to authors, than when they will remain anonymous. One recent study revealed reviewers in five journals who voluntarily signed their reviews gave more positive recommendations than those who did not sign their reviews. We replicate and extend this finding by analyzing 12010 open reviews in PeerJ and 4188 reviews in the Royal Society Open Science where authors can voluntarily sign their reviews. These results based on behavioral data from real peer reviews across a wide range of scientific disciplines demonstrate convincingly that reviewers' decision to sign is related to their recommendation. The proportion of signed reviews was higher for more positive recommendations, than for more negative recommendations. We also share all 23649 text-mined reviews as raw data underlying our results that can be re-used by researchers interested in peer review.
}

@@

PeerJ assigns all articles a number, increasing consecutively with each published manuscript. Reviews are always accessible in HTML (e.g., reviews for the first article published in PeerJ are available at \url{https://peerj.com/articles/1/reviews}). For Royal Society Open journals reviews are published online as a PDF file. A list of Digital Object Identifiers (DOIs) for every article published in RSOS and RSOB was retrieved through Scopus. All available reviews were downloaded, and the PDF files were converted to plain text files using pdftools for R (Ooms, 2020; R Core Team, 2013). These text files were mined for recommendations, reviewer names, submission and acceptance dates, and the review content, using the stringr package in R (Wickham, 2019).

For each article we extracted the number of revisions, and for each revision we saved whether each of the reviewers signed, the word count for their review, and their recommendation for that review round. Note that for PeerJ the editor makes the recommendation for each submission based on the reviews. We therefore do not directly know which recommendation each reviewer provided, but we analyze the data based on the assumption that the decision by the editor is correlated with the underlying reviews. For Royal Society Open journals reviewers make a recommendation, which may be to \enquote{accept as is}, \enquote{accept with minor revisions}, \enquote{major revision}, or \enquote{reject}. Because PeerJ and Royal Society Open journals only share reviews for published articles there are few \enquote{reject} recommendations for Royal Society Open journals and no \enquote{reject} recommendations by editors among PeerJ reviews. Searching all reviews for PeerJ for the words \enquote{appealed on} revealed 47 articles that were initially rejected, appealed, received a \enquote{major revision} recommendation, and were eventually published. We have coded these papers as \enquote{major revisions}. All scripts to download and analyze the reviews, and computationally reproduce this manuscript, are available at \url{https://osf.io/9526a/}.

@@

Analyzing the reviews at Royal Society Open journals provides a more direct answer to our question, since each individual reviewer is asked to provide a recommendation of \enquote{accept}, \enquote{minor revisions}, \enquote{major revisions}, or \enquote{reject}. We can therefore directly compare how recommendations are related to the decision to sign reviews (see Figure \ref{fig:TRSrec}). The overall pattern clearly shows that the proportion of signed reviews is larger for more positive recommendations (accept and minor revisions) whereas the proportion of unsigned reviews is larger for more negative reviews (major revisions and reject).

@@

Both PeerJ and Royal Society Open journals publish articles in a wide range of disciplines. The open reviews at PeerJ specify the subject area the article was submitted to, but this information is not available from meta-data or the bibliographic record for Royal Society Open journals.

@@

To examine the extent to which there is variation in signed and unsigned reviews across subject areas in PeerJ, Figure \ref{fig:PeerJrecperfield} shows the number of signed and unsigned reviews, as a function of the recommendation provided by the editor, across 11 subject areas (and one left-over category for articles not assigned a section). We see that the general pattern holds across all fields. In general, reviews are less likely to be signed than unsigned, except for the paleontology and evolutionary science section, where reviews are more likely to be signed than unsigned. Beyond this main effect, we see a clear interaction across all sections, where the ratio of signed versus unsigned reviews is consistently greater for major revisions than for minor revisions. Across all fields covered by PeerJ, it is relatively less likely to see a signed review for major revisions than for minor revisions, suggesting that the observed effect is present across disciplines.

Figure \ref{fig:recperyear} shows the number of signed and unsigned reviews as a function of the recommendation for each year in which articles were published (since 2012 for PeerJ, and since 2014 for Royal Society Open journals). As already noted, the proportion of signed reviews reduced over time compared to earlier analyses by Wang et al. (2016). Figure \ref{fig:recperyear} reveals that this conclusion holds for both PeerJ and Royal Society Open journals. It seems that in the early years of their existence more reviewers who accepted invitations to review for PeerJ and Royal Society Open journals also agreed to sign their reviews. We don't have the data to explain this pattern, but one might speculate that these open access journals attracted authors and reviewers especially interested in transparency and openness when they started to publish manuscripts. As the journals became more established, and the number of submissions increased, the reviewer population increased beyond the early adopters of open science, to include reviewers less likely to sign their reviews.

@@

Regrettably, neither PeerJ nor Royal Society Open journals make peer reviews available for manuscripts that were rejected. As a consequence, we have analyzed a biased sample of the literature. Few scientific journals make peer reviews available for all submitted articles (two notable exceptions are Meta-Psychology and F1000). Although open reviews enable us to look in more detail at the peer review process, it would be extremely interesting to be able to follow manuscripts through the peer review process even when they are rejected at one specific journal. Despite this limitation, the pattern of results we observe is very similar to that reported by Bravo et al. (2019) who had access to the reviews for accepted and rejected manuscripts.

@@

\hypertarget{author-contributions}{%
\subsection{Author Contributions}\label{author-contributions}}

@@

\hypertarget{conflict-of-interest-statement}{%
\subsection{Conflict of Interest Statement}\label{conflict-of-interest-statement}}

@@

\hypertarget{funding}{%
\subsection{Funding}\label{funding}}

@@

\hypertarget{orcid-id}{%
\subsection{ORCID ID}\label{orcid-id}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bastian_signing_2018}{}%
Bastian, H. (2018). Signing critical peer reviews and the fear of retaliation: What should we do? \textbar{} Absolutely Maybe. https://blogs.plos.org/absolutely-maybe/2018/03/22/signing-critical-peer-reviews-the-fear-of-retaliation-what-should-we-do/.

@@

\leavevmode\hypertarget{ref-ooms_pdftools_2019}{}%
Ooms, J. (2020). \emph{Pdftools: Text extraction, rendering and converting of pdf documents}. Retrieved from \url{https://CRAN.R-project.org/package=pdftools}

@@

\leavevmode\hypertarget{ref-wickham_stringr_2019}{}%
Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
